\documentclass[11pt,letterpaper,sans]{moderncv} 
\usepackage{multibib}
%list here the desired bibliographies
\newcites{pubs,work}{{Published papers},{Unpublished work}}

\moderncvstyle{classic} 
% style options are 'casual', 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}
% color options 'blue', 'orange', 'green', 'red', 'purple', 'grey' and 'black'
% adjust size
\usepackage[scale=0.75]{geometry}
% personal data

\firstname{Stefano}
\familyname{Allesina}
\address{Department of Ecology \& Evolution\\ 
         University of Chicago,\\ 
         1101 E. 57th St.}
        {Chicago, IL 60637 USA} 
        \phone{+1~(773)~702~7825} 
\fax{+1~(111)~111~1111}   
\email{sallesina@uchicago.edu}     
\homepage{allesinalab.uchicago.edu}

\begin{document}
\makecvtitle

\section{Education}
\cventry{1995--2001}
        {Laurea}
        {University of Parma}{Italy}
        {EnvironmentalSciences}
        {}
\cventry{2002--2005}
        {Ph.D.}
        {University of Parma}
        {Italy}
        {Ecology}
        {}

\section{Academic Appointments}
\cventry{2009--}
        {Assistant Professor}
        {University of Chicago}
        {Chicago, IL}
        {Dept. Ecology \& Evolution, Computation Institute}
        {}
        
\cventry{2007--2009}
        {Postdoctoral Associate}
        {NCEAS}
        {Santa Barbara, CA}
        {}
        {}
        
\cventry{2005--2007}
        {Postdoctoral Fellow}
        {University of Michigan}
        {Ann Arbor, MI}
        {Pascual Lab.}
        {}
        
\cventry{2004--2005}
        {Postdoctoral Fellow}
        {Michigan State University/NOAA}
        {Ann Arbor, MI}
        {Peacor Lab.}
        {}

\section{Publications}
%% The idea is to have different bibliographies for published papers,
%% submitted papers and other pubs
\textit{Member} and \textit{\underline{Undergraduate Member}} of the
Allesina Lab. $^\dagger$ Equal contribution.


\nocitepubs{
  Chris2,
  BayesNet,
  Dimensions,
  John2,
  Nestedness,
  Konrad,
  NewsAndViews,
  StabilityCriteria,
  PeerReview,
  Cities2,
  BodiniCities,
  Taxonomy,
  Chris,
  Ana,
  CarlosSex,
  ADBM,
  Nepotism,
  Ferrarini,
  RPS,
  Seregenti,
  JOSE,
  Alex}

\bibliographystylepubs{unsrt}
\bibliographypubs{publications}

\nocitework{Stability2,
  Modularity,
  GBU}
\bibliographystylework{unsrt}
\bibliographywork{publications}

\section{Support}
\cventry{9/12 -- 8/17}{CAREER: Scientific Computing for a New
  Generation of Ecologists}{\$599,244 NSF DEB \#1148867, PI: S. Allesina}{}{}{}

\cventry{8/10 -- 7/14}{Bacteria test biodiversity
  theories}{\$449,817 James S. McDonnell Foundation, PI: S. Allesina
  Co-PI: J. Bergelson}{}{}{}

\cventry{8/10 -- 7/14}{Accelerating the pace of discovery by changing
  the peer review algorithm}{\$240,073 NSF SMA SBE EAGER 
  \#1042164, PI: S. Allesina}{}{}{}

\cventry{9/08 -- 8/14}{The Spider and the
Web: inference in ecological networks}{\$636,000 NSF EF \#0827493,
PI: M. Pascual Co-PI: S. Allesina}{}{}{}

\section{Service}
\subsection{Editorial Board}
\cventry{2009 --}{Subject Editor}{Oikos}{}{}{}
\cventry{2011 --}{Population Ecology}{Faculty of 1000}{}{}{}
\cventry{2012 --}{Associate Editor}{Journal of Complex Networks}{}{}{}
\cventry{2013 --}{Editor Reviewer}{Frontiers in Computational Physics}{}{}{}
\cventry{2012, 2013}{Guest Editor}{PLoS Computational Biology}{}{}{}

\subsection{Reviewer}
\cvitem{Reviewer for}{American Naturalist; Basic and Applied
Ecology; Behavioral Ecology; Biology Letters; Briefings in
Bioinformatics; Chaos; Ecography; Ecological Complexity; Ecological
Indicators; Ecological Modelling; Ecological Monographs; Ecology;
Ecology Letters; Environmental Modelling \& Assessment; Environmental
Modelling \& Software; Estuarine, Coastal and Shelf Science; Fisheries
Research; Journal of Animal Ecology; Journal of Robust and Nonlinear
Control; Journal of Theoretical Biology; Journal of the Royal Society
Interface; Marine Ecology Progress Series; Marsden Fund -- Royal
Society of New Zealand; Methods in Ecology \& Evolution; Microsoft
Research; National Science Foundation; Nature; Nature Communications;
Nature Methods; NERC; Oikos; Philosophical Transactions of the Royal
Society Series B; Physics Letters A; PLoS Biology; PLoS One;
Proceedings of the National Academy of Sciences USA; Proceedings of
the Royal Society Series B; Science; Sinauer Publishing; Theoretical
Ecology; Theoretical Population Biology; The Quarterly Review of
Biology; Romanian National Council for Scientific Research; Scientific
Reports; Trends in Ecology \& Evolution; Trends in Parasitology;
U. California Press; U. Chicago Press; U. Nebraska Omaha Internal
Funding.}

\section{Honors \& Awards}

\section{Mentoring}
\cvitem{Graduate Students}{Si Tang (2010-2013), Elizabeth Sander
  (2012-), Matthew Smith (2013-), Linnea Jones (2013-)}

\cvitem{Postdocs}{Anna Ekl\"of (2010-2012), Phillip Staniczenko
  (2011-2013), Samraat Pawar (2012-2013)}

\cvitem{Undergrad.}{Jose
  Rojas (2009-2010), Alex Zook (2009-2010), Philip Reinhold
  (2010-2011), M Moore (2010-2011), Jason Kopp (2011-2012), Matthew
  Smith (2012-2013), Michael Begun (2012-), Cody Weinberger (2013-)}

\section{Teaching}

\section{Talks \& Seminars}

\cvitem{Dec 5, 2013}{\emph{University of California Davis}, Davis,
  CA. \emph{Dept. Seminar}}
\cvitem{Nov 13, 2013}{\emph{Food Webs: Science for Impact}, Giessen,
  Germany. \emph{Keynote Speaker}}
\cvitem{Oct 12, 2013}{\emph{Society of Population Ecology}, Sakai,
  Japan. \emph{Keynote Speaker}}
\cvitem{Apr 22, 2013}{\emph{University of Puerto Rico -- Rio Piedras}, San Juan, Puerto Rico. \emph{Invited}}
\cvitem{Mar 14, 2013}{\emph{iDiv}, Leipzig, Germany. \emph{Invited}}
\cvitem{Nov 1, 2012}{\emph{University of Oxford}, Oxford, UK. \emph{Invited}}
\cvitem{Sept 24, 2012}{\emph{University of Ume\r{a}},   Ume\r{a},
  Sweden. \emph{Dept. Seminar}}
\cvitem{Sept 14, 2012}{\emph{University of Michigan},  Ann Arbor, MI. \emph{Invited}}
\cvitem{June 23, 2012}{\emph{NetSci 2012},  Evanston, IL. \emph{Invited}}
\cvitem{June 7, 2012}{\emph{BioM\&S Symposium 2012}, University of Guelph, CA. \emph{Keynote speaker}}
\cvitem{May 14, 2012}{\emph{University of Chicago}, Chicago IL. \emph{Dept. Seminar}}
\cvitem{Apr 26, 2012}{\emph{University of Amsterdam}, Amsterdam, the
  Netherlands. \emph{Keynote speaker}}
\cvitem{Apr 13, 2012}{\emph{University of Toronto - EEB Retreat},  Toronto, CA. \emph{Keynote speaker}}
\cvitem{Apr 6, 2012}{\emph{Case Western Reserve}, Cleveland, OH. \emph{Invited}}
\cvitem{Oct 23, 2011}{\emph{Chicago Humanities Festival},  Chicago, IL. \emph{Invited}}
\cvitem{Sept 15, 2011}{\emph{University of Sao Paulo}, Sao Paulo, Brazil. \emph{Invited}}
\cvitem{Sept 14, 2011}{\emph{University of Campinas, Brazil}, Campinas, Brazil. \emph{Invited}}
\cvitem{Sept 2, 2011}{\emph{Iowa State University}, Ames, IA. \emph{Invited}}
\cvitem{Sept 1, 2011}{\emph{Iowa State University}, Ames,
  IA. \emph{Dept. Seminar}}
\cvitem{Aug 8, 2011}{\emph{Ecological Society of America Annual Meeting}, Austin, TX. \emph{Contributed.}}
\cvitem{July 18, 2011}{\emph{International Environmetrics Society -- Regional Meeting}, La Crosse, WI. \emph{Invited}}
\cvitem{June 2, 2011}{\emph{European Conference on Ecological Modeling},  Riva del Garda, Italy. \emph{Contributed.}}
\cvitem{Sept 7, 2010}{\emph{British Ecological Society Annual Meeting}, Leeds, UK. \emph{Invited}}
\cvitem{Jul 7, 2010}{\emph{Universit\`a di Parma},  Parma, Italy. \emph{Invited}}
\cvitem{Apr 29, 2010}{\emph{1st Spark Reception: Agent-based Modeling. University of Chicago}, Chicago, IL. \emph{Invited}}
\cvitem{Apr 22, 2010}{\emph{University of Michigan CSCS}, Ann Arbor, MI. \emph{Invited}}
\cvitem{Feb 16, 2010}{\emph{University of California Santa Barbara},
  Santa Barbara, CA. \emph{Dept. Seminar}}
\cvitem{Feb 2, 2010}{\emph{University of Illinois at Chicago},
  Chicago, IL. \emph{Dept. Seminar}}
\cvitem{Dec 9, 2009}{\emph{The Northwestern Institute on Complex Systems (NICO)}, Evanston, IL. \emph{Invited}}

\section{Skills}
\cvitem{Languages}{Italian (native speaker), proficient English}
\cvitem{Computer Skills}{C, python, R, \LaTeX, Linux}
\end{document}
